%-------------------------
% Resume in LaTeX
% Author: Jake Gutierrez template, customized for Tran Thanh Quan
% ATS-first revision based on verified project evidence
%-------------------------

\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[utf8]{inputenc}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.55in}
\addtolength{\textheight}{1.05in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \small#2 \\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{
  \begin{itemize}[leftmargin=0.15in, label={}]
}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{
  \begin{itemize}[leftmargin=0.22in]
}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\githublink}[1]{
  \href{#1}{\underline{GitHub}}
}

\newcommand{\evidence}{
  \href{https://drive.google.com/drive/u/0/folders/1LMZj8joTEEtuXSfDAe9V3OUMThsBQ6qx}
  {\underline{Evidence}}
}

%-------------------------------------------
%%%%%% RESUME STARTS HERE %%%%%%%%%%%%%%%%%%
%-------------------------------------------

\begin{document}

%----------HEADING----------

\begin{center}
  \textbf{\Huge \scshape Tran Thanh Quan} \\ \vspace{3pt}
  \small
  Ho Chi Minh City, Vietnam $|$
  0974426058 $|$
  \href{mailto:tranthanhquan09@gmail.com}{\underline{tranthanhquan09@gmail.com}} $|$
  \href{https://github.com/qwan30}{\underline{GitHub}} $|$
  \href{https://www.linkedin.com/in/tran-thanh-quan-eric-78842b326/}
  {\underline{LinkedIn}}
\end{center}

%-----------SUMMARY-----------

\section{Summary}
\small{
Backend-focused Software Engineering student at FPT University (GPA: \textbf{8.0/10}) building Java/Spring Boot and Python/FastAPI systems involving concurrency control, transactional workflows, event-driven integration, RBAC, and permission-aware RAG. Developed evidence-backed projects validated through K6 load scenarios, \textbf{245 backend tests}, \textbf{148 Java tests}, and Playwright/Vitest quality gates. Seeking a \textbf{Backend Engineering Internship/OJT}.
}

%-----------EDUCATION-----------

\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {FPT University}{Ho Chi Minh City, Vietnam}
    {Bachelor of Engineering in Software Engineering -- GPA: \textbf{8.0/10}}
    {Aug. 2023 -- Expected Aug. 2027}
\resumeSubHeadingListEnd

%-----------PROJECTS-----------

\section{Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading
    {\textbf{Inventory Flash Sale System}
    \githublink{https://github.com/qwan30/inventory-flashsale-system}
    $|$ \emph{Java 21, Spring Boot, Redis, Kafka, MySQL, K6}}
    {Mar. 2026 -- Present}
  \resumeItemListStart
    \resumeItem{
      Built a modular Spring Boot inventory platform using \textbf{Redis SKU locks},
      JPA optimistic locking, and idempotency guards to coordinate reservation
      workflows under flash-sale contention.
    }
    \resumeItem{
      Implemented a \textbf{transactional outbox} with Kafka publishing and retry
      states, plus scheduled Shopee and TikTok Shop inventory synchronization and
      drift reconciliation.
    }
    \resumeItem{
      Designed a \textbf{15-table MySQL/Flyway schema} and validated five K6 load
      scenarios---including hot-SKU contention, reservation expiry, outbox recovery,
      and reconciliation---with a \textbf{0\% request-failure rate} in a local benchmark.
    }
  \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{AI Hospital Knowledge Assistant}
    \githublink{https://github.com/qwan30/chat-hospital-system}
    $|$ \emph{FastAPI, Next.js, PostgreSQL, pgvector, Redis, RAG}}
    {Feb. 2026 -- Present}
  \resumeItemListStart
    \resumeItem{
      Built a FastAPI and Next.js hospital knowledge assistant with
      \textbf{permission-filtered RAG} that excludes unauthorized patient data
      before constructing LLM context.
    }
    \resumeItem{
      Implemented buffered streaming and \textbf{citation validation} to reject
      answers containing unsupported evidence, validated through a backend suite
      of \textbf{245 tests}.
    }
    \resumeItem{
      Developed a Redis/RQ document-ingestion pipeline with multi-format loaders,
      chunking, embeddings, hybrid BM25/vector retrieval, failure tracking, and
      hospital-record synchronization.
    }
  \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Hospital Management System}
    \githublink{https://github.com/qwan30/hospital-management-system}
    $|$ \emph{Java 17, Spring Boot, Next.js, PostgreSQL, Docker}}
    {Jul. 2025 -- Present}
  \resumeItemListStart
    \resumeItem{
      Developed a full-stack hospital platform supporting booking, clinical,
      pharmacy, inventory, finance, and patient-portal workflows for
      \textbf{7 roles} across \textbf{118 REST mappings} and \textbf{72 Next.js pages}.
    }
    \resumeItem{
      Structured the backend into \textbf{5 DDD-style Maven modules} and
      \textbf{20 Flyway migrations}, enforcing \textbf{66 method-level authorization
      checks} and protecting patient identifiers with AES-GCM encryption.
    }
    \resumeItem{
      Maintained quality gates with \textbf{148 backend tests},
      \textbf{80.48\% frontend branch coverage}, and \textbf{25 Playwright
      specifications} covering RBAC, booking, queue, clinical, and visual-regression
      workflows.
    }
  \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------LEADERSHIP & ACTIVITIES-----------

\section{Leadership \& Activities}
\resumeSubHeadingListStart

  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]
    {@{}p{0.80\textwidth}@{\extracolsep{\fill}}r@{}}
    \small\textbf{Tet Luon Vui -- Community Fundraising Project}
    $|$ \emph{Communications \& Logistics, SSG104}
    & \small\evidence{} $|$ 2026 \\
  \end{tabular*}\vspace{-7pt}

  \resumeItemListStart
    \resumeItem{
      Coordinated communications and logistics for a \textbf{9-member}
      student-led fundraising project, managing visual content, online promotion,
      sales operations, and event execution; grew its Facebook page from
      \textbf{0 to 900+ followers} and increased net funds raised by
      \textbf{254.5\%}.
    }
  \resumeItemListEnd

  \vspace{-2pt}\item
  \small{
    \textbf{Competitions}: FPT Student Mathematics Olympic (Feb. 2025);
    SEAL Hackathon (2025).
  }\vspace{-5pt}

\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Languages}{: Java, Python, TypeScript, JavaScript, SQL} \\
    \textbf{Backend \& Architecture}{: Spring Boot, FastAPI, REST APIs,
      JPA/Hibernate, Maven, RBAC, Idempotency, Concurrency Control,
      Transactional Outbox} \\
    \textbf{Frontend}{: React, Next.js} \\
    \textbf{Data \& Messaging}{: PostgreSQL, MySQL, Redis, pgvector, Kafka, Flyway} \\
    \textbf{DevOps \& Testing}{: Docker, Docker Compose, GitHub Actions,
      JUnit, Pytest, Playwright, Vitest, K6} \\
    \textbf{AI}{: RAG, Permission-Aware Retrieval, Hybrid Retrieval,
      Citation Validation, LLM Workflows} \\
    \textbf{Certifications}{: \textbf{Architecting Solutions on AWS} (2026),
      \textbf{Retrieval Augmented Generation (RAG)} (2026)}
  }}
\end{itemize}

%-------------------------------------------
\end{document}
